Equations & R Code

### 2017-03-02 manuscript/coexistence-stability_SI.Rmd
adds 8 spp storage effect plot to SI

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \onehalfspacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={small},labelfont={sf,bf},labelsep=space]{caption}
  - \usepackage{tikz}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology_letters.csl

@@

>>>>

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \onehalfspacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={normalsize},labelfont={bf},labelsep=quad]{caption}
  - \usepackage{tikz}
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology_letters.csl

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=4in]{./components/regional_diversity_stability_storage_effect_8species.png}
  \caption{A storage effect result.}
\end{figure}
